Near infrared spectrum of a Class 0 protostar photosphere

### 2017-05-04 document/ms.tex
Update the ms table with description of experiments

\tabcolsep=0.11cm
%\rotate
\tablecaption{Exeriment log \label{tbl_history}}
\tablewidth{0pt}
\tablehead{
\colhead{Exp.} &
\colhead{Run.} &
\colhead{Desc.} &
\colhead{Outcome}
\\
\colhead{\#} &
\colhead{\#} &
\colhead{-} &
\colhead{-}
}
\startdata
 1 & 1 & Original, flawed \texttt{star\_veil.py} code modeled disk radiance as a constant value with no physical interpretation & Exposed need for more physical inputs \\
2 & 1 & Run with \texttt{star\_BB.py} code with erroneous $\Omega$ prescription, weak priors, poor first guess & Exposed need for better priors and starting guess \\
2 & 2 & Run with \texttt{star\_BB.py} code with erroneous $\Omega$ prescription, strong priors ($T_{d}$ fixed to $\sim1100$ K), good first guess & Exposed incorrect $\Omega$ treatment \\
3 & 1 & Run with \texttt{star\_BB.py} code with correct absolute flux level, strong priors ($T_{d}$ fixed to $\sim1100$ K). & Reasonable results, weak constraints on $\logg$. \\
3 & 2 & \emph{In progress:} Run with \texttt{star\_BB.py} code with correct absolute flux level, \emph{weak} priors ($T_{d}$ variable $\in [1000,1700]$ K). & -- \\
4 & 1 & Reduced spectral range to enhance $\logg$ sensitivity & Good convergence, wide range \\
\enddata
\end{deluxetable*}

>>>>

\tabcolsep=0.11cm
%\rotate
\tablecaption{Exeriment log \label{tbl_history}}
\tablewidth{0pt}
\tablehead{
\colhead{Exp.} &
\colhead{Run.} &
\colhead{Desc.} &
\colhead{Outcome}
\\
\colhead{\#} &
\colhead{\#} &
\colhead{-} &
\colhead{-}
}
\startdata
 1 & 1 & Original, flawed \texttt{star\_veil.py} code modeled disk radiance as a constant value with no physical interpretation & Exposed need for more physical inputs \\
2 & 1 & Run with \texttt{star\_BB.py} code with erroneous $\Omega$ prescription, weak priors, poor first guess & Exposed need for better priors and starting guess \\
2 & 2 & Run with \texttt{star\_BB.py} code with erroneous $\Omega$ prescription, strong priors ($T_{d}$ fixed to $\sim1100$ K), good first guess & Exposed incorrect $\Omega$ treatment \\
3 & 1 & Run with \texttt{star\_BB.py} code with correct absolute flux level, strong priors ($T_{d}$ fixed to $\sim1100$ K). & Reasonable results, weak constraints on $\logg$. \\
3 & 2 & Run with \texttt{star\_BB.py} code with correct absolute flux level, \emph{weak} priors ($T_{d}$ variable $\in [1000,1700]$ K). & -- \\
4 & 1 & Reduced spectral range to enhance $\logg$ sensitivity & Good convergence, wide posteriors \\
5 & 1 &  Windowing on CO and Na~I, $T_{d}$ fixed to $\sim1100$ K & Slightly higher $T_{\mathrm{eff}}$ and $\log{g}$ compared to just CO window.\\
6 & 1 &  Introduce $A_V$, with fixed ($\chi=-2.0$) slope, $\log{g}>2.0$, Chebyshev $6\%$ peak-to-valley & Tighter $T_{eff}$ and $\log{g}$ posteriors than before\\
7 & 1 &  $A_V$, with variable ($\chi \in [-2.0, -1.7]$) slope, $\log{g}>2.0$, Chebyshev $2\%$ peak-to-valley & Tighter $T_{eff}$ and $\log{g}$ posteriors due to tighter Chebyshev, $\chi$ limit exceeded\\
8 & 1 &  $A_K$, with variable ($\chi \in [-2.0, -1.7]$) slope, $\log{g}>2.0$, Chebyshev $2\%$ peak-to-valley & Re-running\\
\enddata
\end{deluxetable*}
